MaxEnt: What is it good for?

### 2015-06-19 ms.tex
gibbs
Some edits

\section{Probability}
We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $A_1$, $A_2$, ..., $A_N$ which we will usually
think of as possible values of an unknown quantity $x$. For example,
$A_1 \equiv $``$x=1$'', $A_2 \equiv $``$x=2$'', and so on.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true (i.e. the true value of $x$ is in our set),
but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
The standard loose Bayesian notation would write this distribution simply
as $p(x)$.

Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
($A_5$ {\bf or} $A_8$) is $p_5/(p_5 + p_8)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

@@

The relative entropy of distribution $p$ from distribution $q$ is:
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}
and we are to choose the distribution $p$ to maximise $H$ subject to the
constraints of normalisation and any other constraints.

@@

>>>>

\section{Probability}
We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $A_1$, $A_2$, ..., $A_N$ which we will usually
think of as possible values of an unknown quantity $x$. For example,
$A_1 \equiv $``$x=1$'', $A_2 \equiv $``$x=2$'', and so on.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true (i.e. the true value of $x$ is in our hypothesis space),
but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
In the standard loose Bayesian notation we write this distribution simply
as $p(x)$.

Of course, $p(x)$ must be non-negative and sum to 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
($A_5$ {\bf or} $A_8$) is $p_5/(p_5 + p_8)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

@@

The relative entropy of distribution $p$ from distribution $q$ is:
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}
Intuitively, $H$ measures how close the probability distribution $p$ is
to the distribution $q$. The maximum possible value of $H$ is zero, if
and only if $p$ happens to be the same as $q$.
However, it is not symmetric and does not satisfy
other properties of a distance.
and we are to choose the distribution $p$ to maximise $H$ subject to the
constraints of normalisation and any other constraints.

@@

\bibitem[Gibbs(1914)]{gibbs} Gibbs, J.~W.~Elementary Principles in
Statistical Mechanics: Developed with Special Reference to the Rational
Foundations of Thermodynamics. Yale University Press, 1914.
